---
title: "Predictive model for apartments_pl data"
output: 
  html_document:
    toc: true
---

# Read data

Read the data from the kaggle website https://www.kaggle.com/datasets/krzysztofjamroz/apartment-prices-in-poland-2023q3.

```{r warning=FALSE, message=FALSE}
library("randomForest")
apartments_pl <- read.table("apartments_pl_2023q3.csv", sep=",", header = TRUE, stringsAsFactors = TRUE)
```

# Data Preprocessing

Change characters into factors.

```{r warning=FALSE, message=FALSE}
library(missMethods)
set.seed(1)

apartments_pl_filled <- impute_median(apartments_pl)
apartments_pl_filled$price <- apartments_pl_filled$price / apartments_pl_filled$squareMeters

head(apartments_pl_filled)
```


# Create a gbm model

Let's use `gbm` library to create a `gbm` model with 250 trees 3 levels deep.

```{r warning=FALSE, message=FALSE}
library("gbm")
set.seed(1)

model <- gbm(price~.-latitude-longitude, data = apartments_pl_filled)
```

# Create a DALEX explainer

Let's wrap gbm model into a DALEX explainer.

```{r warning=FALSE, message=FALSE}
library("DALEX")
model_explained <- explain(model, apartments_pl_filled, y = apartments_pl_filled$price)
```

# Feature Importance explainer

Calculate Feature Importnace explainer.

```{r warning=FALSE, message=FALSE}
library("ingredients")
library("auditor")
fi <- feature_importance(model_explained)
plot(fi)
```


# modelStudio app

Calculate modelStudio dashboard.

```{r eval = FALSE}
library(modelStudio)
op <- ms_options(
  subtitle = "Price of an appartment"
)
modelStudioApartments <- modelStudio(model_explained, 
                  new_observation = apartments_pl_filled[sample(1:nrow(apartments_pl_filled), 25),-c(8,9,27)],
                  options = op)
modelStudioApartments

r2d3::save_d3_html(modelStudioApartments, file = "index.html")
```

